Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-06-03 nlpcc/paper.tex

\begin{abstract}
Cross-lingual Knowledge Bases are important for global knowledge sharing. However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the number of current cross-lingual language links is limited; 3) the incorrect relation in semantic taxonomy. In this paper, a large-scale cross-lingual knowledge base(CLKB) is build to solve the above problems. The CLKB is based on English and Chinese Wikipedia as well as Baidu Baike and Hudong Baike. An extension method is used to increase language links while a pruning approach is used to refine taxonomy. Totally, there are XXX classes, XXX instances, XXX properties referred in the CLKB. Moreover, the paper provides visualization webpages of knowledge and a SPARQL endpoint accessing to the established CLKB.

@@

\subsection{Cross-lingual Knowledge Base Building}
In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources. Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting. We then enrich the extracted language-link set $CL$ using an link-discovery extension method. We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.

@@

However, the whole taxonomy can not directly transform from category system because of the following problems:
\begin{itemize}
    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
    %s\item Some sub-category links in the category system maybe inconsistent. Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it. As Fig. \ref{fig:category-mistakes} shows: In Hudong, the sub-category of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree. Meanwhile, in Wikipedia, \textcolor{red}{例子}
    \item Some categories relate to only one or two articles. According to the definition of class, such categories are less representative to a group of instances, therefore it's unwise to retain it as class.
\end{itemize}
   To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original class hierarchy $H^C$ using the remaining categories.

@@

\section{Cross-lingual Integration}
\label{sec:clkbb}
To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from class relationships to make it more accurate. At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.

\subsection{Cross-lingual Linking}
There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

@@

\subsection{Taxonomy Prune}
\label{sec:tp}
As a result of combining multi-source information without verifying, the taxonomy of class system is mussy. For example, \textcolor{red}{example}. Therefore, we introduce the method from\cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}. Table. \ref{tab:} shows some examples of correct relations. In particular, some language-dependent literal and language-independent structural features are defined to vectorize each class or instance. Employing these features, a Yes-or-Not binary-classification model is trained based on Logistic Regression. The whole process is iterative by retraining model with assured result to get higher precision. Confirming a right \textit{subClassOf} or \textit{instanceOf} not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.

@@

\section{Conclusion}
\label{sec:con}
This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources. At first, we extract structured information and unify data format. Then a cross-lingual language link set is generated to help combine the bilingual sources. Besides, an extension method is applied to enrich the links. To refine our dataset, we also conduct pruning work on taxonomy. Finally, we acquire a knowledge base containing XXX classes, XXX instances and XXX properties. Currently, a SPARQL query interface is provided to access the knowledge base.

>>>>

\begin{abstract}

Cross-lingual Knowledge Bases are important for global knowledge sharing. However, there are few Chinese-English knowledge bases due to the following reasons: 1) the scarcity of Chinese knowledge; 2) the number of current cross-lingual language links is limited; 3) the incorrect relation in semantic taxonomy. In this paper, a large-scale cross-lingual knowledge base(CLKB) is build to solve the above problems. The CLKB is based on English and Chinese Wikipedia as well as Baidu Baike and Hudong Baike. An extension method is used to increase language links while a pruning approach is used to refine taxonomy. Totally, there are XXX classes, XXX instances, XXX properties referred in the CLKB. Moreover, the paper provides visualization webpages of knowledge and a SPARQL endpoint accessing to the established CLKB.

@@

\subsection{Cross-lingual Knowledge Base Building}

In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources. Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting. We then enrich the extracted language-link set $CL$ using an link-discovery extension method. We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.

@@

However, the whole taxonomy can not directly transform from category system because of the following problems:
\begin{itemize}
    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
    %s\item Some sub-category links in the category system maybe inconsistent. Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it. As Fig. \ref{fig:category-mistakes} shows: In Hudong, the sub-category of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree. Meanwhile, in Wikipedia, \textcolor{red}{例子}
    \item Some categories relate to only one or two articles. According to the definition of class, such categories are less representative to a group of instances, therefore it's unwise to retain it as class.
\end{itemize}

   To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original class hierarchy $H^C$ using the remaining categories.

@@

\section{Cross-lingual Integration}
\label{sec:clkbb}

To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate. At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.

\subsection{Cross-lingual Linking}
There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label. That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.

@@

\subsection{Taxonomy Prune}
\label{sec:tp}

As a result of combining multi-source information without verifying, the taxonomy of class system is mussy. For example, \textcolor{red}{example}. Therefore, we introduce the method from\cite{wang2014cross} to detect the correct \textit{subClassOf} and \textit{instanceOf} relations from \textit{subCategoryOf} and \textit{articleOf}. Table. \ref{tab:} shows some examples of correct relations. In particular, some language-dependent literal and language-independent structural features are defined to vectorize each class or instance. Employing these features, a Yes-or-Not binary-classification model is trained based on Logistic Regression. The whole process is iterative by retraining model with assured result to get higher precision. Confirming a right \textit{subClassOf} or \textit{instanceOf} not only depends on the prediction result of classification, but also cross-lingual knowledge validation, which ensures correctness if both the mapped English and Chinese relations are correct.

@@

\section{Conclusion}
\label{sec:con}

This paper presents a procedure of building a Chinese-English cross-lingual knowledge base from four encyclopedia sources. At first, we extract structured information and unify data format. Then a cross-lingual language link set is generated to help combine the bilingual sources. Besides, an extension method is applied to enrich the links. To refine our dataset, we also conduct pruning work on taxonomy. Finally, we acquire a knowledge base containing XXX classes, XXX instances and XXX properties. Currently, a SPARQL query interface is provided to access the knowledge base.
